---
title: "Sample statistics"
output: 
  html_document:
    css: "www/LlibreBST.css"
    toc: true
    toc_float:
      toc_collapsed: true
    toc_depth: 3
    number_sections: true
    # theme: united
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, message=FALSE, comment='',warning = FALSE)
```

# Introduction

```{r echo=T}
library(tidyverse)
library(rmarkdown)
library(summarytools)
 
```

# Basic Exploratory Data Analysis

## Data: Chicken Weights by Feed Type

An experiment was conducted to measure and compare the effectiveness of various feed supplements on the growth rate of chickens. Results are in a data frame **chickwts** with two variables:

- weight: a numeric variable giving the chick weight.
- feed: a factor giving the feed type.

```{r}
data(chickwts)
chickwts %>% paged_table()
```

## Compute basic statistics

```{r}
chickwts %>% 
  group_by(feed) %>%
  descr(weight) 
```

```{r}
chickwts %>% 
  group_by(feed) %>%
  descr(weight,stats = "common") %>%
  tb() %>%
  select(-variable) %>%
  knitr::kable()
```


```{r}
chickwts %>% 
  group_by(feed) %>% 
  summarise(Mean=round(mean(weight),1),sd=round(sd(weight),1),N=n()) %>% 
  knitr::kable()
```


```{r}
ggplot(chickwts,aes(feed,weight,fill=feed))+
  geom_boxplot()
```


```{r}
ggplot(chickwts,aes(feed,weight,fill=feed))+
  geom_boxplot() +
  coord_flip()
```

```{r}
ggplot(chickwts,aes(feed,weight,color=feed))+
  stat_summary(fun.data=mean_cl_normal)
```

```{r}
ggplot(chickwts,aes(weight,fill=feed))+
  geom_histogram(binwidth = 50,color='black')+
  facet_wrap(.~feed)
```


```{r}
ggplot(chickwts,aes(weight))+
  geom_histogram(aes(y=..density..,,fill=feed),
                 binwidth = 50,color='black')+
  geom_density()+
  facet_wrap(.~feed)
```







# Compute some statistics

